ACNP 2024 MS ANXIETY

### 2024-08-30 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
added back the promis analysis

#fishers exact:  p-value = 0.1313, 95 % CI 0.7169704 7.4524239, OR 2.388734 
fisher_test <- fisher.test(df_2x2_promis_score_by_total_people_per_diagnosis)
print(fisher_test)
```
#### Plot promis x anxiety dose
```{r plot_Promis_x_anxiety}
#set mood versus physical domains
mood_domains <- c("Quality_of_Life", 
                "Mental_Health_and_Mood",
                "Social_Activities_Satisfaction",
                "Carrying_Out_Social_Activities",
                "Emotional_Problems", 
                "PostOp.PROMIS.Mental.Score")

@@

#### Plot 
#####Promis x anxiety dose, group by mental vs physical health
```{r plot_Promis_x_anxiety}
#set mood versus physical domains
mood_domains <- c("Mental_Health_and_Mood",
                "Social_Activities_Satisfaction",
                "Carrying_Out_Social_Activities",
                "Emotional_Problems", 
                "Quality_of_Life",
                "PostOp.PROMIS.Mental.Score")

@@

@@

#### Uncinate by anxiety diagnosis (vol and prop)
```{r uncinate_by_dx}
### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group

>>>>

#fishers exact:  p-value = 0.1313, 95 % CI 0.7169704 7.4524239, OR 2.388734 
fisher_test <- fisher.test(df_2x2_promis_score_by_total_people_per_diagnosis)
print(fisher_test)
```

#### Plot 
##### Plot promis x anxiety dose
```{r plot_Promis_x_anxiety}
#set mood versus physical domains
mood_domains <- c("Quality_of_Life", 
                "Mental_Health_and_Mood",
                "Social_Activities_Satisfaction",
                "Carrying_Out_Social_Activities",
                "Emotional_Problems", 
                "PostOp.PROMIS.Mental.Score")

@@

#####Promis x anxiety dose, group by mental vs physical health
```{r plot_Promis_x_anxiety}
#set mood versus physical domains
mood_domains <- c("Mental_Health_and_Mood",
                "Social_Activities_Satisfaction",
                "Carrying_Out_Social_Activities",
                "Emotional_Problems", 
                "Quality_of_Life",
                "PostOp.PROMIS.Mental.Score")

@@

```
####Test promis*anxiety dose  stats
#####Physical and Mental Health together
```{r phsy_and_mental_step_x_anxiety_dose}
###
df_for_promis_plot_mental_vs_physical_healthy_test <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
  mutate(phys_mental_diff_score = physical_health_score-mental_health_score) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                physical_health_score,
                mental_health_score,
                phys_mental_diff_score)

#looking at anxiety_dose = 2 only, 0.22 -> sample size too small

mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_vs_physical_health_t

#looking at physical health and mental health in sick vs healthy

#physical health, sick vs healthy - t = 2.0048, df = 8.6555, p-value = 0.07722
physical_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
physical_health_t_sick_vs_healthy

#mental health, sick vs healthy - t = 3.6838, df = 8.1324, p-value = 0.006011
mental_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_health_t_sick_vs_healthy

###linear models
#anxiety_dose  -0.7345     0.2946  -2.493   0.0153 * ; (T = -2.493, P = 0.015, Cohen's f2 =  0.1, Effect size = small)
anxiety_dose_x_phys_score <- lm(physical_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_phys_score)
lm_summary_stats(lm_model = anxiety_dose_x_phys_score, which_variable = 2)

#anxiety_dose  -1.1181     0.2681  -4.171 9.59e-05 ***; (T = -4.171, P = 0, Cohen's f2 =  0.281, Effect size = medium)
anxiety_dose_x_mental_score <- lm(mental_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_mental_score)
lm_summary_stats(lm_model = anxiety_dose_x_mental_score, which_variable = 2)

#anxiety_dose   0.3836     0.2391   1.605    0.114; (T = 1.605, P = 0.114, Cohen's f2 =  0.042, Effect size = small) - delta between physical and mental health NS
anxiety_dose_x_diff_score <- lm(phys_mental_diff_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_diff_score)
lm_summary_stats(lm_model = anxiety_dose_x_diff_score, which_variable = 2)

@@

#### Uncinate by anxiety diagnosis (prop)
```{r uncinate_by_dx}
### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group
